Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-07 draftfinalreport_v4.Rnw
11:17 update figure captions to remove reference to proportion to vaccinate

\begin{figure}
     \centering
     \includegraphics[width=0.9\textwidth]{figures/sim.pdf}
     \caption{A subset of the expected number of measles cases from 1000 simulations of a model (\autoref{section:epidemic_modelling}) in a homogeneously mixed population in New Zealand with 28\% of the currently 11\% susceptible to measles infection immunised, using an $R_v$ <1. The full distribution of rare results can be seen in \autoref{fig:sim1}.}
     \label{fig:sim}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.9\textwidth]{figures/sim1.pdf}
  \caption{The distribution of the expected number of measles cases from 1000 simulations of a model (\autoref{section:epidemic_modelling}) in a homogeneously mixed population in New Zealand with 28\% of the currently 11\% susceptible to measles infection immunised, using an $R_v$ <1, showing the rare but possible large epidemic sizes possible. 
  Note this figure does not show the frequency of common events as the y-axis was limited to 20 to show rare events. The full distribution of common results can be seen in \autoref{fig:sim}.}
     \label{fig:sim1}
\end{figure}

>>>>

\begin{figure}
     \centering
     \includegraphics[width=0.9\textwidth]{figures/sim.pdf}
     \caption{A subset of the expected number of measles cases from 1000 simulations of a model (\autoref{section:epidemic_modelling}) in a homogeneously mixed population in New Zealand using an $R_v$ <1. The full distribution of rare results can be seen in \autoref{fig:sim1}.}
     \label{fig:sim}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=0.9\textwidth]{figures/sim1.pdf}
  \caption{The distribution of the expected number of measles cases from 1000 simulations of a model (\autoref{section:epidemic_modelling}) in a homogeneously mixed population in New Zealand using an $R_v$ <1, showing the rare but possible large epidemic sizes possible. 
  Note this figure does not show the frequency of common events as the y-axis was limited to 20 to show rare events. The full distribution of common results can be seen in \autoref{fig:sim}.}
     \label{fig:sim1}
\end{figure}
